\cvsection{Work Experience}
\begin{cventries}
  \cventry
    {Software Architect \& Global Technical Lead}
    {Cloud Network Services, IBM}
    {Shanghai, China}
    {Dec. 2012 - Present}
    {
      \begin{cvitems}
        \item {Lead the architecture design and implementation of GSLB service on IBM Bluemix cloud.}
        \item {Lead the architecture design and implementation of DNS service on IBM Bluemix Cloud.}
        \item {Lead and Deputy People Manager of IBM China SDN/NFV appliances development team for DHCP/DNS, VPN, and IDS/IPS appliances.}
        \item {Design and implement the Layer 2 VLAN \& Q-in-Q for IBM Next Generation switch OS.}
        \item {Develop a self-inspired innovation on automation testing benchmark and educate team to use the platform.}
        \item {Lead the internal Eagle technical virtual team to track the state-of-the-art technologies in networking and cloud.}
        \item {Filed 6 patents and IDT review board member.}
      \end{cvitems}
    }
  \cventry
    {Senior Software Engineer \& ASIC Architecture Designer}
    {Centec Networks}
    {Suzhou, Jiangsu, China}
    {Dec. 2007 - Dec. 2012}
    {
      \begin{cvitems}
        \item {ASIC architecture research and design w/ a wide variety of hardware implementation of features across ACL, QoS, Data Center Virtualization, SDN/OpenFlow, and algorithms on Dynamic Load Balancing (DLB), Packet Classification, Long Prefix Matching (LPM), and Hierarchical Metering.}
        \item {SDK development of ACL, QoS, H-QoS, CPU Traffic Protection and Statistics for new generation of switch chips.}
        \item {System software development of ACL, Statistics, QoS, H-QoS features on Ethernet switches.}
        \item {Filed 3 patents.}
        %\begin{cvsubentries}
          %\cvsubentry{}{KNOX(Solution for Enterprise Mobile Security) Penetration Testing}{Sep. 2013}{}
          %\cvsubentry{}{Smart TV Penetration Testing}{Mar. 2011 - Oct. 2011}{}
        %\end{cvsubentries}
      \end{cvitems}
    }
\end{cventries}
