\cvsection{Skills}
\begin{cventries}
  \cventry
    {Programming Language}
    {}
    {}
    {}
    {
      \begin{cvitems}
        \item {Fluent in Linux C and Python.}
        \item {Good understanding of C++, Java, Tcl and Object-orient programming.}
        \item {Familar of data modeling languages: JSON, YAML, XML.}
      \end{cvitems}
    }

    \cventry
    {Cloud}
    {}
    {}
    {}
    {
      \begin{cvitems}
        \item {Develop experience with OpenStack Neutron and Designate projects.}
        \item {Develop experience on IBM Bluemix Cloud.}
        \item {Good understanding of IaaS, PaaS, and SaaS.}
        \item {Good understanding of RESTful design, Cloud Native, Microservice, Serverless, Immutable Infrastructure, Auto Scaling, NoSQL, etc.}
        \item {Familiar with some other cloud platforms: Cloud Foundry, Docker, Kubernetes, etc.}
        \item {Familiar with some virtualization technologies: KVM, VMware, etc.}
      \end{cvitems}
    }

    \cventry
    {DevOps \& Mastering Tools}
    {}
    {}
    {}
    {
      \begin{cvitems}
        \item {Experience with Docker, Vagrant, Ansible, Git and Jenkins to build the full chain of DevOps.}
        \item {Experience with troubleshooting tools such as GDB, PDB, Tcpdump, Valgrind, etc.}
        \item {Experience with Git, SVN, and RTC version control systems.}
        \item {Familiar with a variety of documentation tools: \LaTeX{}, MS Office, Markdown, ReStructured Text, etc.}
      \end{cvitems}
    }
    
    \cventry
    {Networking Technology}
    {}
    {}
    {}
    {
      \begin{cvitems}
        \item {Solid understanding of Ethernet switching and TCP/IP protocols.}
        \item {Develop and research experiences top-down TCP/IP stack.}
      \end{cvitems}
    }
\end{cventries}
